---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

# Mean, Median, Range

The goal of the MeanMedianRange package is to provide documentation and
create a downloadable R package for the mean_median_range function that
was created in Assignment B1 in STAT 545. This function calculates the
mean, median and range values for any numerical dataset.

### Overview of Package Structure

This R Package follows the standard structure of an R package

-   DESCRIPTION File: Contains a brief description of the file, the
    version of the package, information on the author, and the license.

-   man Folder: Contains a '.RD' file that is generated by the roxygen2
    documentation to highlight the function's purpose, parameters,
    output, and examples to show how to use the function. The '.RD' file
    can be viewed using: ?mean_median_range

-   NAMESPACE File: Specifies which function in this package is
    available for others to use.

-   R Folder: Contains the R script files with the code for the
    mean_median_range function

-   README File: Provides an overview of the package and contains
    information on the different files and folders in the package, as
    well as installation instructions and examples.

-   LICENSE Files: Contains the license documentation for this package

### Installation

You can install the development version of MeanMedianRange from
[GitHub](https://github.com/) with:

``` r
install_github("stat545ubc-2024/assignment-b2-laurasimonson/MeanMedianRange")
```

### Example

This function can be used for datasets that contain NA values and
datasets that do not contain NA values. This function can also be used
in a set of numbers that you create and with an already existing
dataset.

Function code:
```{r}
mean_median_range <- function(x, na.rm = FALSE){
  if(!is.numeric(x)){
    stop("Input is not numeric, this function requires numeric values.")
    }
  a = mean(x, na.rm = na.rm)
  b = median(x, na.rm = na.rm)
  c = range(x, na.rm = na.rm)
  c(a,b,c(c))
}
```


Example 1: With NA Values

```{r example}
mean_median_range(c(1, 2, 3, 4, 5, NA, 6), na.rm = TRUE)
```

In this example dataset, the mean is 3.5, the median is 3.5 and the
range is between 1.0 and 6.0.

Example 2: Without NA Values

```{r}
mean_median_range(c(10, 20, 30, 40, 50))
```

In this example dataset without any NA values, the mean is 30, the
median is 30, and the range is between 10 and 50.

Example 3: Already Existing Dataset

```{r}
library(palmerpenguins)
mean_median_range(penguins$body_mass_g, na.rm = TRUE) 
```

Using an already existing dataset containing information on penguins, we
can find that the mean of the body_mass_g category is 4201.754 the
median is 4050, and the range of the body_mass_g category is between
2700 and 6300.
